Paper 1 GLM

### 2018-10-10 Vitis_GLM.Rmd
acerifolia tt breakpoint SUCCESS

We ran a LM for leaf number and total teeth.
```{r}
acerifolia <-filter(R_DiLP_all_species, species == "acerifolia")
skim(acerifolia, total.teeth)
ac_tt_plot <- ggplot(acerifolia, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic()
ac_tt_plot <- ac_tt_plot +labs(x = "Leaf number",
                               y = "Total teeth")
ac_tt_plot

```

```{r}
ac_tt_lm <- lm(total.teeth ~ leaf, data = acerifolia)
summary(ac_tt_lm)
```

```{r}
ac_tt_seg <- segmented(ac_tt_lm,
                       seg.Z = ~ leaf,
                       psi = NA)
summary(ac_tt_seg)
```

>>>>

We ran a LM for leaf number and total teeth.
```{r}
acerifolia <-filter(Vitis_90_ratios, species == "acerifolia")
skim(acerifolia, total.teeth)
ac_tt_plot <- ggplot(acerifolia, aes(x = leaf, y = total.teeth)) + geom_smooth() + theme_classic() + scale_x_continuous(breaks = seq(0, 12, 1))
ac_tt_plot <- ac_tt_plot +labs(x = "Leaf number",
                               y = "Total teeth")
ac_tt_plot

```
We need the means for each leaf character for both years combined.
```{r}
ac_l_means <-  acerifolia %>% 
  group_by(leaf) %>% 
  summarize(avg.tt = mean(total.teeth),
            avg.fdr = mean(feret.diameter.ratio),
            avg.tap = mean(tooth.area.perimeter, na.rm = TRUE),
            avg.taip = mean(tooth.area.int.perimeter, na.rm = TRUE),
            avg.ta = mean(average.tooth.area, na.rm = TRUE),
            avg.taba = mean(tooth.area.blade.area, na.rm = TRUE),
            avg.tp = mean(teeth.perimeter),
            avg.tip = mean(teeth.int.perimeter),
            avg.pa = mean(perimeter.area),
            avg.pr = mean(perimeter.ratio),
            avg.cp = mean(compactness),
            avg.sf = mean(shape.factor),
            avg.tba = mean(teeth.blade.area))
```

```{r}
ac_tt_mean_plot <- ggplot(ac_l_means, aes(x = leaf, y = avg.tt)) + geom_line() + theme_classic()
ac_tt_mean_plot <- ac_tt_mean_plot +labs(x = "Leaf number",
                               y = "Total teeth")
ac_tt_mean_plot
```

```{r}
ac_tt_lm <- lm(avg.tt ~ leaf, data = ac_l_means)
summary(ac_tt_lm)
```

```{r}
ac_tt_seg <- segmented(ac_tt_lm,
                       seg.Z = ~ leaf,
                       psi = list(leaf = c(2, 7)))
summary(ac_tt_seg)
```

```{r}
ac_tt_seg$psi
slope(ac_tt_seg)
ac_tt_fitted <- fitted(ac_tt_seg)
ac_tt_model <- data.frame(Leaf = ac_l_means$leaf, Teeth = ac_tt_fitted)
ggplot(ac_tt_model, aes(x = Leaf, y = Teeth)) + geom_line()
ac_tt_lines <- ac_tt_seg$psi[, 2]
ac_tt_mean_break <- ac_tt_plot + geom_vline(xintercept = ac_tt_lines, linetype = "dashed")
ac_tt_mean_break
```
